Interfacing logic programming and Coq

### 2020-10-26 papers/types2020/sec3.tex
some small progress on sec 4
adding file for conclusion
some work on fig 1

\begin{metanote}
  add proof terms and backchaining to sequents and code -- now sig is commented out
\end{metanote}
\begin{footnotesize}
\begin{figure}
\newcommand{\XXi}{{\color{blue}{\Xi}}}
\[
\infer{\XXi\vdash t = t}
      {\eqExpert{\XXi}}
\qquad
\infer{\XXi\vdash \true}
      {\trueExpert{\XXi}}
\qquad
\infer{\XXi\vdash G_1\vee G_2}
      {\XXi'\vdash G_i\qquad \orExpert{\XXi}{\XXi'}{i}}
\qquad
\infer{\XXi\vdash \exists x. G}
      {\XXi'\vdash G[t/x]\qquad \someExpert{\XXi}{\XXi'}{t}}
\]
\vskip -6pt
\[
\infer{\XXi\vdash G_1\wedge G_2}
      {\XXi_1\vdash G_1\quad \XXi_2\vdash G_2\quad \andExpert{\XXi}{\XXi_1}{\XXi_2}}
\qquad
\infer{\XXi\vdash A}
      {\XXi'\vdash G \quad (A~\hbox{\tt :-}~G)\in\instan\Pscr
                     \quad \unfoldExpert{\XXi}{\XXi'}}
\]
\caption{A proof system augmented with proof certificates and
  additional ``expert'' premises.}
\label{fig:augmented}
%\lstinputlisting[linerange={sigs-end}]{code/dep-kernel.sig}
\lstinputlisting[linerange={check-end}]{code/dep-kernel.mod}
\caption{A simple proof checking kernel.}
\label{fig:kernel}
\end{figure}
\end{footnotesize}
Figure~\ref{fig:augmented} contains a simple proof system for Horn
clause provability in which each inference rule is augmented with an
additional premise involving an \emph{expert predicate}, a
certificate $\Xi$, and possibly continuations of certificates ($\Xi'$,
$\Xi_1$, $\Xi_2$) with extracted information from certificates (in the
case of $\vee$ and $\exists$).
%
%
% 
Although this proof system is a focused proof system, the
richness of focusing is not apparent in this simplified 
setting: thus, we drop the adjective ``focused'' from this point forward.

@@

\begin{metanote}
  Rethink and update (with the right connectives) these FPC
\end{metanote}
\begin{figure}
\lstinputlisting[linerange={resources-end}]{code/fpcs.sig}
\lstinputlisting[linerange={resources-end}]{code/fpcs.mod}
\caption{Two FPCs that describe proofs that are limited in either
  height or in size.}
\label{fig:resources}
\end{figure}

>>>>

\begin{footnotesize}
\begin{figure}
  \newcommand{\XXi}{}
  \newcommand{\bc}[2]{#1 >\!> #2}
\[
\infer{\XXi\vdash t = t}
{%\eqExpert{\XXi}
}
\qquad
\infer{\XXi\vdash \true}
{%\trueExpert{\XXi}
}
\qquad
\infer{\XXi\vdash G_1\vee G_2}
{\XXi\vdash G_i%\qquad \orExpert{\XXi}{\XXi'}{i}
}
\qquad
\infer{\XXi\vdash \exists x. G}
{\XXi\vdash G[t/x]%\qquad \someExpert{\XXi}{\XXi'}{t}
}
\qquad 
\infer{\XXi\vdash G_1\wedge G_2}
{\XXi\vdash G_1\quad \XXi\vdash G_2%\quad \andExpert{\XXi}{\XXi_1}{\XXi_2}
}
\qquad
\infer{\XXi\vdash A}
      {\bc D A \quad D \in \Pscr}
\]
\vskip -18pt
\[
  \infer{\bc A A}{}{}\qquad
  \infer{\bc{\forall x.\, D} A}{\bc{D[t/x]} A}{}\qquad
  \infer{\bc{G\supset D} A}{\bc D A\quad \XXi\vdash G}{}
\]
\lstinputlisting[linerange={interp-end}]{code/dep-kernel.mod}
\caption{A proof system for Horn logic and its encoding in coq-elpi .}
\label{fig:augmented}
%\lstinputlisting[linerange={sigs-end}]{code/dep-kernel.sig}
\lstinputlisting[linerange={check-end}]{code/dep-kernel.mod}
\caption{A dependent kernel for Coq terms.}
\label{fig:kernel}
\end{figure}
\end{footnotesize}
Figure~\ref{fig:augmented} contains a simple proof system for Horn
clause provability in which each inference rule is augmented with an
additional premise involving an \emph{expert predicate}, a
certificate $\Xi$, and possibly continuations of certificates ($\Xi'$,
$\Xi_1$, $\Xi_2$) with extracted information from certificates (in the
case of $\vee$ and $\exists$).
%
%
% 
Although this proof system is a focused proof system, the
richness of focusing is not apparent in this simplified 
setting: thus, we drop the adjective ``focused'' from this point forward.

@@

\begin{figure}
\lstinputlisting[linerange={resources-end}]{code/fpcs.sig}
\lstinputlisting[linerange={resources-end}]{code/fpcs.mod}
\caption{Two FPCs that describe proofs that are limited in either
  height or in size.}
\label{fig:resources}
\end{figure}
